Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-17 reanalysis-4-outcome_analysis.qmd
emmeans

    # Find the probability column (could be "prob", "response", "emmean", etc.)
    prob_col <- names(df_probs)[grep("prob|response|emmean", names(df_probs), ignore.case = TRUE)[1]]
    se_col <- names(df_probs)[grep("SE|se", names(df_probs))[1]]

    # Standardize column names
    df_probs$prob <- df_probs[[prob_col]]
    df_probs$SE <- df_probs[[se_col]]

>>>>

    # Debug: print column names for first iteration
    if (i == 1) {
      message("emmeans response columns: ", paste(names(df_probs), collapse = ", "))
    }

    # The response scale should have columns like: prob, asymp.LCL, asymp.UCL, SE
    # Or it might be: response, asymp.LCL, asymp.UCL, SE
    # Find the main estimate column
    prob_col <- if ("prob" %in% names(df_probs)) {
      "prob"
    } else if ("response" %in% names(df_probs)) {
      "response"
    } else if ("emmean" %in% names(df_probs)) {
      "emmean"
    } else {
      # Just use the first numeric column that's not a CI
      numeric_cols <- names(df_probs)[sapply(df_probs, is.numeric)]
      numeric_cols[!grepl("CL|CI|df|SE", numeric_cols)][1]
    }

    # Find SE column
    se_col <- if ("SE" %in% names(df_probs)) {
      "SE"
    } else if ("se" %in% names(df_probs)) {
      "se"
    } else {
      # Calculate from confidence intervals if available
      NULL
    }

    # Standardize column names
    df_probs$prob <- if (!is.null(prob_col)) df_probs[[prob_col]] else NA
    df_probs$SE <- if (!is.null(se_col)) {
      df_probs[[se_col]]
    } else if (all(c("asymp.LCL", "asymp.UCL") %in% names(df_probs))) {
      # Approximate SE from CI width
      (df_probs$asymp.UCL - df_probs$asymp.LCL) / (2 * 1.96)
    } else {
      0.1  # Default SE if we can't calculate it
    }
